---
title: "Marriage on the Rise"

author: 
  - Elizabeth Luong
thanks: "Code and data are available at: ."
date: today
date-format: long
abstract: "This paper examines the trends in marriage licenses issued in Toronto over the past 13 years. By analyzing data from OpenDataToronto using Python for data processing and visualization, several interesting patterns emerge. Notably, a significant increase in marriages is observed immediately following the COVID-19 pandemic in 2021. Seasonal trends are also highlighted, revealing that marriage rates tend to peak during the summer months. This study sheds light on how societal events and seasonality influence marriage behaviors."
bibliography: references.bib
execute:
  echo: false
format: pdf
number-sections: true
---

```{python}
<<<<<<< HEAD
=======
#| echo: false
#| warning: false
#| label: Fig-1
import pandas as pd
import matplotlib.pyplot as plt
import seaborn as sns
from pathlib import Path

current_dir = Path.cwd()
file_path = current_dir.parent / 'data' /'analysis_data'/ 'cleaned_marriage_data.csv'
# Sample DataFrame
data = pd.read_csv(file_path)


df = pd.DataFrame(data)

# Plotting the average marriage licenses by month
plt.figure(figsize=(10, 6))
sns.lineplot(data=data, x='TIME_PERIOD', y='MARRIAGE_LICENSES', marker='o')
plt.title('Average Marriage Licenses by Month')
plt.xlabel('Month-Year')
plt.ylabel('Average Number of Licenses')
plt.grid(True)
plt.xticks(data['TIME_PERIOD'][::24],rotation=45)
plt.tight_layout()

# Display the plot
plt.show()

```

@Fig-1 shows how many interesting trends have been observed in the number of marriage licenses over the past 13 years. The first visible trend is how many marriages there have been since COVID-19, prior to COVID-19 there were between 100 and 700 marriages a month, however, immediately afterwards in 2021, it reached above 1750 in one month. This makes sense but it is also super cool.  We also see that on average, the summer months have a lot more marriages.  Very interesting trends!


#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
```


# Introduction

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....



# Data {#sec-data}

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
>>>>>>> 4eb8cc29a4d3256df8c31f218ab87f87059ea7b6
#| echo: false
#| warning: false
#| label: Fig-1
import pandas as pd
import matplotlib.pyplot as plt
import seaborn as sns
from pathlib import Path

current_dir = Path.cwd()
file_path = current_dir.parent / 'data' /'analysis_data'/ 'cleaned_marriage_data.csv'
# Sample DataFrame
data = pd.read_csv(file_path)


df = pd.DataFrame(data)

# Plotting the average marriage licenses by month
plt.figure(figsize=(10, 6))
sns.lineplot(data=data, x='TIME_PERIOD', y='MARRIAGE_LICENSES', marker='o')
plt.title('Average Marriage Licenses by Month')
plt.xlabel('Month-Year')
plt.ylabel('Average Number of Licenses')
plt.grid(True)
plt.xticks(data['TIME_PERIOD'][::24],rotation=45)
plt.tight_layout()

# Display the plot
plt.show()

```

@Fig-1 shows how many interesting trends have been observed in the number of marriage licenses over the past 13 years. The first visible trend is how many marriages there have been since COVID-19, prior to COVID-19 there were between 100 and 700 marriages a month, however, immediately afterwards in 2021, it reached above 1750 in one month. This makes sense but it is also super cool.  We also see that on average, the summer months have a lot more marriages.  Very interesting trends!

